---
title: "Results"
author: "Loong Kuan"
date: "16 September 2016"
output: html_document
---

```{r setup, echo = FALSE}
options(width=80)
knitr::opts_chunk$set(echo = FALSE, out.width='750px', dpi=200)
library(knitr)
library(ggplot2)
library(ggrepel)
library(reshape2)
library(gridExtra)
library(grid)
library(foreign)
read_chunk("../read_data.R")
read_chunk("../result_table.R")
read_chunk("../distance_matrix.R")
read_chunk("../visualisation.R")
read_chunk("../compare_distributions.R")
read_chunk("../coditioned_covariates.R")
```




## Original Data of 2 Dates
```{r}
<<arff>>
```


Load the satellite data set on the day *2013-05-05* and *2013-11-29*.
```{r load_satellite}
file1 <- "../../datasets/train_seed/20130505.arff"
file2 <- "../../datasets/train_seed/20131129.arff"
data.all <- ReadArffData(file1, file2)
```
Data from *2013-05-05*.
```{r}
print(head(data.all[[1]], 5))
```
Data from *2013-11-29*.
```{r}
print(head(data.all[[2]], 5))
```

Histogram of the data by attributes.
```{r, echo = FALSE}
<<visualisation>>
<<compare>>
  Histogram(data.all[[1]], data.all[[2]])
```


## Drift Results
The raw data of the results will be provided at the end of this document.
```{r, include=F}
<<results>>
  results.prior.1 <- ResultTable("../../data_out/martvard/20130505_20131129_1-attributes_prior.csv")
  results.prior.2 <- ResultTable("../../data_out/martvard/20130505_20131129_2-attributes_prior.csv")
  results.cc.1 <- ResultTable("../../data_out/martvard/20130505_20131129_1-attributes_ConditionedCovariate.csv")
  results.pos.1 <- ResultTable("../../data_out/martvard/20130505_20131129_1-attributes_posterior.csv")
```

### Covariate Drift
The following is the results for a test of 1 Attribute. 
We can verify the correctness of the results by comparing them to the histograms of the attributes above.

```{r}
<<visualisation>>
  SingleHistogramVisual(results.prior.1)
```

From the results above, we can observe that the value distribution of the **id_class** attributes does not change.
Logically, this makes sense if the crop designgnation for each area is constant over the year.

-----------------------------------------

The following is the covariate results for 2 Attributes.
This plot is just an exercise on how results from larger amounts of attributes might be visualised.

The plot is made by first constructing a "distance matrix" where the distance obtained for each pair of attribute is represneted.

```{r}
<<visualisation>>
<<distance_matrix>>
  attributes.all <- ExtractAttributes(results.prior.2)
  distanceMatrix <- DistanceMatrix(results.prior.2)
  print(distanceMatrix)
```

This matrix is then plotted using Multidimensional Scaling to visualise the distances in the matrix.
The final plot will then plot attributes that have a higher dirft together further apart.

```{r}
  MDS(distanceMatrix, attributes.all)
```

From the MDS above, we can observe that, as expected the 2 highest drifters, 
**band5** and **brightness** are pretty far away from most other attributes.


We can also plot the distance matrix as a heatmap to directly view the results. 
However this method only works with 2 attribute tests.
```{r}
  DualHistogramVisual(results.prior.2)
```



### Conditioned Covaraites (Single Attributes)
```{r}
<<covar>>
  JointVisualisation(results.cc.1)
```
We can observe that attributes **band 5** and **brightness** drifts greater than other attributes for most given classes.
Furthermore, most attributes given classes **other_oilseed** and **sunflower** seems to drift between the 2 dates.

### Posterior (1 Attribute)
For the posterior results of 1 attribute, all of the results show *0* posterior drift between the 2 dates.

## Raw Data
### Covariate Drift (1 Attribute)
```{r}
print(results.prior.1)
```

### Covariate Drift (2 Attribute)
```{r}
print(results.prior.2)
```

### Coditioned Covariate Drift (1 Attribute)
```{r}
print(results.cc.1)
```

### Posterior (1 Attribute)
```{r}
print(results.pos.1)
```

--------------------------------------------------------------------------------

